\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-16 experience.tex

Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The model is written once
to include all behaviours of Fabric
so that it can be used again and again to test arbitrary Fabric services.
This was the largest among the case studies
and required multiple rounds of debugging.
The availability of systematic testing
allowed us to debug the model to
a point where reported assertion violations indicate a bug in the
user service.
Without systematic testing,
even bugs in the model would have been hard to find.
Note that we model the lowest Fabric API layer (\texttt{Fabric.dll})
which is not documented for use externally.
Eventually, we will lift the model
to higher layers
but for this paper we study internally-developed services
that directly target the the lowest layer.

@@

The main system that we tested is \emph{CScale}~\cite{X},
a big data-stream processing system that chains multiple Fabric services
in a directed acyclic graph.
A key challenge was that
CScale contains inter-service communication.
%\PTComment{Cut: detail.}
% that resolves services
% via Fabric but communicates
% using a non-Fabric remote procedure call protocol.
In order to close the system,
%\PTComment{Cut: we implemented service resolution}
% we first implemented service resolution in our Fabric model,
% which resolves Fabric service names to IP addresses.
%We then replaced 
we replaced
the inter-service communication
classes in CScale with our own;
our replacement includes the ability to map
URLs to \psharp{} machines
so that remote procedure calls are now implemented
by sending and receiving \psharp{} events.
Thus,
we converted a distributed system
that uses both Fabric and its own
network communication protocol
% that runs on the Fabric platform
% and 
% uses network communication
into 
a closed single process system. 
% that uses multiple threads,
% contains
% the Fabric model
% and the CScale services,
% and does not use network communication.
%\PTComment{Cut: we had to remove static fields.}
% Additional changes were needed to
% remove certain static (per-process) fields,
% as these were inadvertently
% being shared between services
% after making the system a single process.
A key challenge in our work
was to test CScale despite the fact that it
uses various synchronous and asynchronous APIs
other than \psharp{}.
This work is still in-progress.
However,
we were able to find a \texttt{NullReferenceException}
bug
in CScale
by running it on our model.

>>>>

Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The model is written once
to include all behaviours of Fabric
so that it can be used again and again to test arbitrary Fabric services.
This was the largest among the case studies
and required multiple rounds of debugging.
The availability of systematic testing
allowed us to debug the model to
a point where reported assertion violations indicate a bug in the
user service.
Without systematic testing,
even bugs in the model would have been hard to find.
Note that we model the lowest Fabric API layer (\texttt{Fabric.dll})
which is not documented for use externally.
Eventually, we will lift the model
to higher layers
but for this paper we study internally-developed services
that target the lowest layer.

@@

The main system that we tested is \emph{CScale}~\cite{X},
a big data-stream processing system that chains multiple Fabric services
in a directed acyclic graph.
A key challenge was that
CScale contains inter-service communication.
%\PTComment{Cut: detail.}
% that resolves services
% via Fabric but communicates
% using a non-Fabric remote procedure call protocol.
To close the system,
%\PTComment{Cut: we implemented service resolution}
% we first implemented service resolution in our Fabric model,
% which resolves Fabric service names to IP addresses.
%We then replaced 
we 
replaced the relevant classes
% replaced the inter-service communication classes with our own,
% ;
% our replacement includes the ability to map
% URLs to \psharp{} machines
so that remote procedure calls are implemented
by sending and receiving \psharp{} events.
Thus,
we converted a distributed system
that uses both Fabric and its own
network communication protocol
% that runs on the Fabric platform
% and 
% uses network communication
into 
a closed single process system. 
% that uses multiple threads,
% contains
% the Fabric model
% and the CScale services,
% and does not use network communication.
%\PTComment{Cut: we had to remove static fields.}
% Additional changes were needed to
% remove certain static (per-process) fields,
% as these were inadvertently
% being shared between services
% after making the system a single process.
A key challenge in our work
was to test CScale despite the fact that it
uses various synchronous and asynchronous APIs
other than \psharp{}.
This work is still in-progress.
However,
we were able to find a \texttt{NullReferenceException}
bug
in CScale
by running it on our model.
